\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{amsthm, amsmath, amssymb, mathrsfs, mathtools, booktabs, array, graphicx, caption, enumitem, listings, setspace, upgreek}

\newcommand{\Z}{\mathcal{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\bx}{\textbf{x}}


\addtolength{\oddsidemargin}{-.875in}
\addtolength{\evensidemargin}{-.875in}
\addtolength{\textwidth}{1.75in}

\addtolength{\topmargin}{-.875in}
\addtolength{\textheight}{1.75in}

\title{Wackerly Section 1.1 Problems}
\author{John Nguyen}

\begin{document}
\maketitle

\subsection*{Problem 1.1}
    \begin{enumerate}[label=(\alph*).]
        \item 
        \begin{itemize}
            \item Population: Generation X U.S. citizens
            \item Inferential Objective: Proportion of population interested in starting their own business.
            \item Sample: Surveys via mail and in person interviews.
        \end{itemize}
        
        \item 
        \begin{itemize}
            \item Population: Healthy adults
            \item Inferential Objective: Average temperature of the population.
            \item Sample: Medical records from check ups.
        \end{itemize}
        
        \item 
        \begin{itemize}
            \item Population: Single family dwelling units (problem does not explicitly state these units are in use, but we will assume there is a family living in there).
            \item Inferential Objective: Average weekly water consumption.
            \item Sample: Check water meters weekly. For apartments, divide water meter value by the number of single family dwelling units in use.
        \end{itemize}
        
        \item 
        \begin{itemize}
            \item Population: Tires of a specific company, made in a specific year.
            \item Inferential Objective: Proportion of unsafe tread among the population.
            \item Sample: Auditing manufacturing factories via random inspection.
        \end{itemize}
        
        \item 
        \begin{itemize}
            \item Population: Adult residents of a particular state.
            \item Inferential Objective: Proportion of population that prefer unicameral legislature.
            \item Sample: Online and in person surveys/polls. Propose to be on the upcoming ballot.
        \end{itemize}
        
        \item 
        \begin{itemize}
            \item Population: Infected individuals.
            \item Average recurrence time for a disease.
            \item Sample: Medical data from check ups and trials. 
        \end{itemize}
        
        \item 
        \begin{itemize}
            \item Population: Transistors of a certain type.
            \item Inferential Objective: Truth value of: 'average life of population members $>$ 500 hours'
            \item Sample: Run a large sample of these transistors for 500 hours. Then calculate the proportion still alive after 500 hours. If the proportion is greater than 0.5, then the Inferential Objective is True. Otherwise the Inferential Objective is False.
        \end{itemize}
        
        
        
    \end{enumerate}
\end{document}